---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r init, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

qrencoder uses `libqrencode` to make QR codes in R

I have no idea why you would want to, but this was to help answer a question on StackOverflow.

The following functions are implemented:

- `qrencode`:	Return a QR encoded string as a matrix
- `qrencode_df`:	Return a QR encoded string as an x, y, z data.frame
- `qrencode_png`:	Return a QR encoded string as a base 64 encoded inline png
- `qrencode_raster`:	Return a QR encoded string as a raster object

NOTE: You'll need `Rcpp`, `base64enc`, `raster` & `png` installed (and, `libqrencode` of course). 

Not tested under Windows.

### News

- Version  released

### Installation

```{r show, eval=FALSE}
devtools::install_github("hrbrmstr/qrencoder")
```

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r qr}
library(qrencoder)
library(raster)

# current verison
packageVersion("qrencoder")

url <- "http://rud.is/b"
head(qrencode(url))

head(qrencode_df(url))

qrencode_png(url)

qrencode_raster(url)

par(mar=c(0,0,0,0))
image(qrencode_raster("http://rud.is/b"), 
      asp=1, col=c("white", "black"), axes=FALSE, 
      xlab="", ylab="")
```

### Test Results

```{r, test}
library(qrencoder)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
