---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r init, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

`qrencoder` : Make QR codes in R

There is another package on CRAN -- `qrcode` -- that is not C-backed.

Quick Response codes (QR codes) are a type of matrix bar code and can be
used to authenticate transactions, provide access to multi-factor authentication
services and enable general data transfer in an image. QR codes use four standardized 
encoding modes (numeric, alphanumeric, byte/binary, and kanji) to efficiently store 
data. Matrix barcode generation is performed efficiently in C via the included
'libqrencoder' library created by Kentaro Fukuchi.

The following functions are implemented:

- `qrencode`:	Return a QR encoded string as a matrix
- `qrencode_df`:	Return a QR encoded string as an x, y, z data.frame
- `qrencode_png`:	Return a QR encoded string as a base 64 encoded inline png
- `qrencode_raster`:	Return a QR encoded string as a raster object
- `qrencode_svg`:	Return a QR encoded string as an svg string

### Installation

```{r show, eval=FALSE}
devtools::install_github("hrbrmstr/qrencoder")
```

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r qr}
library(qrencoder)

# current verison
packageVersion("qrencoder")

url <- "http://rud.is/b"
head(qrencode(url))

head(qrencode_df(url))

qrencode_png(url)

qrencode_raster(url)

par(mar=c(0,0,0,0))
image(qrencode_raster("http://rud.is/b"), 
      asp=1, col=c("white", "black"), axes=FALSE, 
      xlab="", ylab="")
```

### SVG

```{r qrsvg}
cat(qrencode_svg(url))
```

![](https://rud.is/dl/qr.svg)

### Test Results

```{r, test}
library(qrencoder)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
